My title

### 2024-04-01 paper/paper.qmd
updated codes, cleanings, and more graphs for paper analyses

#### Load data ####
GSS <- read_parquet(here::here("data/analysis_data/cleaned_GSS.parquet"))
demo_data <- read_parquet(here::here("data/analysis_data/demo_data.parquet"))
days_data <- read_parquet(here::here("data/analysis_data/days_data.parquet"))
depress_data <- read_parquet(here::here("data/analysis_data/depress_data.parquet"))
mentalVsHealth <- read_parquet(here::here("data/analysis_data/mentalVsHealth_data.parquet"))
```

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].

@@

## Demographic Variables 
```{r}
#| label: tbl-data-overview
#| tbl-cap: Overview of the Demographic Data 
#| echo: false
#| warning: false
#| message: false

@@

kable(head(demo_data), 
      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Group", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

## Demographic Variables

@@

@@

@@

>>>>

#### Load data ####
GSS <- read_parquet(here::here("data/analysis_data/cleaned_GSS.parquet"))
demo_data <- read_parquet(here::here("data/analysis_data/demo_data.parquet"))
days_data <- read_parquet(here::here("data/analysis_data/days_data.parquet"))
analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
mentalVsHealth <- read_parquet(here::here("data/analysis_data/mentalVsHealth_data.parquet"))
```

@@

@@

The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], `arrow` [@arrow], and `knitr` [@knitr].

@@

## Demographic Variables 
```{r}
#| label: tbl-demo-overview
#| tbl-cap: Overview of the Demographic Data 
#| echo: false
#| warning: false
#| message: false

@@

kable(head(demo_data), 
      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Groups", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

## Mental and Physical Unwellness and Depression Diagnosis
```{r}
#| label: tbl-analysis-vars
#| tbl-cap: Overview of the Main Analysis Dataset
#| echo: false
#| warning: false
#| message: false

vars <- c("ID","Physical Unwellness","Mental Unwellness","Depression Diagnosis")

kable(head(analysis_data), 
      caption = "Counted days of Physical and Mental unwellness with Depression Diagnosis", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

## Mental Unwellness and General Health Status
```{r}
#| label: tbl-health-vars
#| tbl-cap: Overview of the Mental Unwellness vs. General Health Status Dataset 
#| echo: false
#| warning: false
#| message: false

vars <- c("ID","Mental Unwellness","General Health")

kable(head(mentalVsHealth), 
      caption = "Counted days of Mental unwellness with General Health Status", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

## Non-response Rate

??? maybe include a table of non-response rate

Some of the questions in the dataset are not included resulting no responses collected in certain years, while the other responses were collected. This fact requires extra attention when cleaning and handling since the number of available responses will decrease when additional variables are added. Hence, an additional sub set of the data that only includes counted days of mental and physical un-wellness in the past 30 days is also included for only speculating these two variables.

```{r}
#| label: tbl-sub-vars
#| tbl-cap: Overview of the Mental and Physical Unwellness
#| echo: false
#| warning: false
#| message: false

vars <- c("ID","Physical Unwellness","Mental Unwellness")

kable(head(days_data), 
      caption = "Counted days of Mental unwellness with General Health Status", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

@@

## Depression Playing an Role
```{r}
#| label: fig-mental-vs-physical
#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
#| echo: false
#| warning: false
#| message: false

#Modify depress status for visualization
analysis_data$depress <- as.character(analysis_data$depress)
analysis_data <- mutate(analysis_data,
               depress = case_when(
                 depress == "1" ~ "Yes",
                 depress == "2" ~ "No",
                 TRUE ~ depress
               )
            )

#Graph
analysis_data|>
  ggplot(aes(x = ment_days, y = phys_days, color = depress)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "Mental Unwellness", y = "Physical Unwellness", color = "Depress") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
\break

## Mental Health and Health in General
```{r}
#| label: fig-mental-vs-general
#| fig-cap: Counts of Days Feeling Unwell in Last 30 Days
#| echo: false
#| warning: false
#| message: false

#Graph
mentalVsHealth|>
  ggplot(aes(x = ment_days, y = health)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "Mental Unwellness", y = "General Health") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
\break

## Model Results
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```
